---
output:
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
    keep_tex: true
header-includes:
    - \usepackage{caption}
    - \usepackage{lmodern}
params:
  pkg_scores: "`r list()`"
  mitigation_block: "r NULL"
  risk_breaks: "`r c(0.3, 0.7)`"
  set_title: "Scorecard"
title: "`r params$set_title`"
subtitle: 'MPN Scorecard'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.height = 8, fig.width = 10, ft.keepnext = FALSE)
library(dplyr)
library(flextable)
# set_flextable_defaults(font.color = "#333333", border.color = "#999999", padding = 4, fonts_ignore = TRUE)
set_flextable_defaults(font.color = "#333333", border.color = "#999999", padding = 4, fonts_ignore = TRUE)
```

```{r setup_data}
formatted_pkg_scores <- params$pkg_scores
risk_breaks <- params$risk_breaks # TODO: I think we should include the breaks/weightings used somewhere at some point?
metworx_ver <- paste("Metworx", formatted_pkg_scores$metadata$info$env_vars$METWORX_VERSION)
```

<!-- Remove 'Table x:' prefixes -->
\captionsetup[table]{labelformat=empty}

<br/>

## Overview

This document contains evidence that `r formatted_pkg_scores$pkg_name` `r formatted_pkg_scores$pkg_version` is validated for use on `r metworx_ver` and contains proof points in support of the principles of Good Practice in Documentation, Testing, Maintenance & Stability, and Transparency & Community, as described in **whatever general MPN doc we create**. 

```{r}
format_overall_scores(formatted_pkg_scores)
```

\newpage

## Details

### Documentation, Maintenance & Transparency
```{r, raw scores}
format_package_details(formatted_pkg_scores)
```

### Testing
```{r}
format_testing_scores(formatted_pkg_scores)
```

\newpage

```{r, results = "asis"}
format_mitigation(params$mitigation_block)
```


## System Info
```{r}
format_metadata(formatted_pkg_scores$metadata)
```
