---
output:
  pdf_document:
    toc: true
    toc_depth: 3
  bookdown::pdf_book:
    citation_package: biblatex
bibliography: ["sum_links.bib"]
biblio-style: "apalike"
link-citations: true
# needed to make footnotes point to full bibliography
csl: https://www.zotero.org/styles/chicago-fullnote-bibliography
# needed to prevent additional bibliography section
suppress-bibliography: true
params:
  overall_risk_summary: "`r list()`"
  set_subtitle: "xxxx-xx-xx"
title: "Scorecard Summary"
subtitle: "`r paste('MPN Snapshot', params$set_subtitle)`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.height = 8, fig.width = 10, ft.keepnext = FALSE)
library(dplyr)
library(flextable)
set_flextable_defaults(font.color = "#333333", border.color = "#999999", padding = 4)
```

```{r setup_data}
risk_summary_df <- params$overall_risk_summary$overall_pkg_scores
metadata <- params$overall_risk_summary$metadata
```


# Summary
This document contains evidence and a summary of proof points for all packages on MPN Snapshot `r params$set_subtitle` in support of Principles of Good Practice in Documentation, Testing, Maintenance & Stability, and Transparency & Community (described in more detail below). Information about the system on which this assessment was performed is included in the System Info section, near the bottom of this document.  

# Background
The process documented here relies heavily on principles articulated by the R Validation Hub^[@R-Validation-Hub], a cross-industry initiative whose mission is to enable the use of R by the bio-pharmaceutical industry in a regulatory setting. 

In their Fall 2022 Biopharmaceutical Report^[@Risk-Assessment-of-R-Packages], the R Validation Hub points to ICH E9^[@ICH-E9], which states that “software used should be reliable, and documentation of appropriate software testing procedures should be available.” 

\newpage

## Principles of Good Practice
As recommended by the R Validation Hub, we take a risk-based approach to assessing individual R packages. We break this down into four broad categories: Documentation, Testing, Maintenance & Stability, and Transparency & Community. Some high-level aspects of these categories are enumerated below.

 - Documentation
    - All user-facing functionality is documented
    - User tutorials and examples are available
    - Documentation is published to a website that users can access
 - Testing
    - Contains a test suite, which covers the user-facing functionality, made available with the source code
    - “Regression” tests are added to cover bugs that are fixed
    - R CMD CHECK is passing
 - Maintenance & Stability
    - Release Notes and/or News that detail changes and bug fixes are made publicly available
    - A formal mechanism exists for submitting and tracking bugs
    - Releases are made as necessary to stay compatible with changes in the broader ecosystem
    - Active development addresses reported bugs and requested features
 - Transparency & Community
    - Source code, documentation, and testing are available for users to review and, when necessary, provide feedback or request changes
    - Any changes made are visible to users and are formally approved by an SME who is familiar with the package
    - An active user community interacts with package maintainers

To be clear, not all packages will have all of these components in place. These are meant to enumerate the principles that are used to assess risk for a particular package.


# Summary of Proof Points

The table below summarizes the proof points for risk assessment of all packages on MPN Snapshot `r params$set_subtitle`. Detailed proof points are presented in a separate document for each package.

```{r}
format_score_summaries(risk_summary_df)
```

\newpage

# System Info
```{r}
format_metadata(metadata)
```

