---
geometry: "left=1.5cm,right=1.5cm,top=2cm,bottom=2cm"
output:
  pdf_document:
    toc: true
    toc_depth: 3
    includes:
      in_header: header.tex
  bookdown::pdf_book:
    citation_package: biblatex
bibliography: ["sum_links.bib"]
biblio-style: "apalike"
link-citations: true
# needed to make footnotes point to full bibliography
csl: https://www.zotero.org/styles/chicago-fullnote-bibliography
# needed to prevent additional bibliography section
suppress-bibliography: true
header-includes:
    - \usepackage{caption}
    - \usepackage{graphicx}
    - \usepackage{fancyhdr}
    - \pagestyle{fancy}
    - \setlength\headheight{24pt}
    - \addtolength{\topmargin}{-4pt}
    - \fancyhead[L]{\includegraphics[width=1.25cm]{mpn_logo.png}}
    - \rfoot{\thepage} 
    - \fancyfoot[R]{Metrum Research Group}
params:
  overall_risk_summary: "`r list()`"
  set_subtitle: "xxxx-xx-xx"
title: "Scorecard Summary"
subtitle: "`r paste('MPN Snapshot', params$set_subtitle)`"
---

\fontsize{11}{15}
\selectfont

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.height = 8, fig.width = 10, ft.keepnext = FALSE)
library(dplyr)
library(flextable)
set_flextable_defaults(font.color = "#333333", border.color = "#999999", padding = 4, fonts_ignore = TRUE)
```

```{r setup_data}
risk_summary_df <- params$overall_risk_summary$overall_pkg_scores
metadata <- params$overall_risk_summary$metadata


metworx_ver <- paste("Metworx", metadata$info$env_vars$METWORX_VERSION)
```


# Summary
This document contains evidence that all packages on MPN Snapshot `r params$set_subtitle` are validated for use on `r metworx_ver` and contains a summary of proof points in support of the Principles of Good Practice in Documentation, Testing, Maintenance & Stability, and Transparency & Community. 

# Principles
The validation process documented here relies heavily on principles articulated by the R Validation Hub^[@R-Validation-Hub], a cross-industry initiative whose mission is to enable the use of R by the bio-pharmaceutical industry in a regulatory setting. 

In their Fall 2022 Biopharmaceutical Report^[@Risk-Assessment-of-R-Packages], the R Validation Hub points to ICH E9^[@ICH-E9], which states that “software used should be reliable, and documentation of appropriate software testing procedures should be available.” Furthermore, both the original 2020 Val Hub white paper and 2020 RStudio paper highlight the need to validate R and its constituent packages for use “in a validated environment.” For this reason, this document specifically validates the named R packages for use on `r metworx_ver`.

\newpage

## Principles of Good Practice
As recommended by the R Validation Hub, we take a risk-based approach to assessing individual R packages. We break this down into four broad categories: Documentation, Testing, Maintenance & Stability, and Transparency & Community. Some high-level aspects of these categories are enumerated below.

 - Documentation
    - All user-facing functionality is documented
    - User tutorials and examples are available
    - Documentation is published to a website that users can access
 - Testing
    - Contains a test suite, which covers the user-facing functionality, made available with the source code
    - “Regression” tests are added to cover bugs that are fixed
    - R CMD CHECK is passing
 - Maintenance & Stability
    - Release Notes and/or News that detail changes and bug fixes are made publicly available
    - A formal mechanism exists for submitting and tracking bugs
    - Releases are made as necessary to stay compatible with changes in the broader ecosystem
    - Active development addresses reported bugs and requested features
 - Transparency & Community
    - Source code, documentation, and testing are available for users to review and, when necessary, provide feedback or request changes
    - Any changes made are visible to users and are formally approved by an SME who is familiar with the package
    - An active user community interacts with package maintainers

To be clear, not all packages will not have all of these components in place. These are meant to enumerate the principles that are used to assess risk for a particular package.

\newpage

# Summary of Proof Points

The table below summarizes the proof points for risk assessment of all packages on MPN Snapshot `r params$set_subtitle`. Detailed proof points are presented in a separate document for each package.

```{r}
format_score_summaries(risk_summary_df)
```

\newpage

# System Info
```{r}
format_metadata(metadata)
```

